Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-09 WRITEUP/ms.tex
polish fig cap and sec 5

The growth of galaxies and their subsequent evolution are governed by the baryon cycle ---
galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes)
and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
The general consensus is that the growth of \highz galaxies are triggered and supported by massive
gas inflows from mergers and/or the cosmic web at early cosmic time, when the IGM and galaxies themselves 
are more gas-rich in their star-forming molecular
gas contents compared to present-day galaxies.
% while at a given snapshot, the gas mass fraction maybe low (esp. at high-z when
% the gravitational potential is still increasing), but their gas reservoirs
% are continuously being replenished.
These massive gas inflows in turn trigger gravitational instability and lead
to the formation of gas structures that are typically more massive and denser than those
observed in nearby galaxies, with masses of $M_{\rm cloud}$\eq10$^9$\,\Msun
and sizes on sub-kpc scales (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
Some theoretical works argue that the
migration of such giant massive clumps are responsible for contributing to the
buildup of the bulges of massive galaxies at \z$\sim$0 \citep[e.g.,][]{Ceverino10a}.

@@

As we increase the density threshold, some of the MC within the main disk break
into multiple sub-MCs.
As such, we effectively identify a population of denser molecular structures  (\Fig{MC}).
This population of sub-MCs has dynamics largely
similar to those observed
in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
e.g., \citealt{Swinbank11a}),
with sizes of the order of $R\simeq$100\,pc and velocity
dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. 
As shown in \Fig{alpha16}, their virial parameter ($\alpha_{\rm vir}\gtrsim10$)
are lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$). 
%We note that previous studies by 
%\citealt{Dobbs08a} and \citealt{Tasker09a} report that
%clouds form in galactic disk typically have virial parameters between $\alpha_{\rm vir}$\eq0.2$-$10.
This is consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally non-collapsing structures,
which are supported by turbulence and rotation.
In fact, based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
would indicate that the MC itself is gravitationally unbound and is supported/confined 
by turbulence and rotation on large scales.
On the other hand, the MCs in the satellite galaxies are found to have
lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
with $\alpha_{\rm vir}\simeq$1 (see top panels of \Fig{alpha16} and \Fig{alpha27}).
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). 
Given the low $\alpha_{\rm vir}$ parameter
and the $\sigma^2/R - \Sigma$ relation found for the MCs of the satellite galaxies, 
these structures are likely collapsing structures.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
\caption{
Larson's (linewidth-size) relation of \flower in
accreting phase (top) and
starburst phase (bottom) compared to
those observed in nearby and the \z$\sim$2 star-forming galaxy.
Red lines show the relation obtained from 
Literature data are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accreting phase (star symbols) compared to those observed in the Milky Way.
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs (star symbols) 
compared to those observed in the Milky Way (black dot markers).
The V-shaped dashed lines show locii along which the given external pressures
are needed in order for MCs to have linewidth $\sigma$ for a given set of surface densities. (see \Sec{PVE})
In both panels, the star symbols are color-coded by the $n_{\rm cut}$ adopted to identify the corresponding MCs.
\label{fig:alpha16}}
\end{figure*}

@@

We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accreting phase (see \Sec{sfh})
compared to the empirical relation obtained based on 
Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein),
which we extrapolate to match the mass and size scales of the MCs of \flower.
By comparing the masses and sizes found in clouds with and without massive \SF ($<$10\,\Msun) 
in the Milky Way, \citet{Kauffmann10c} report a 
mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
at a given radius. As shown in \Fig{MR}, the MCs identified in the accreting phase of \flower lie above this relation, along to the locus 
with visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
parameter space as the accreting phase. 
{\bf so...}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs in \flower compared to data and empirical established based on Milky Way \obs.
Star symbols show MCs identified in the accreting phase of \flower in our simulation, color-coded by increasing $n_{\rm cut}$.
Other symbols show the masses and sizes of molecular clouds with massive \SF observed in the 
Milky Way \citep{Beuther02a, Mueller02a, Hill05a, Motte07a}.
Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
\label{fig:MR}}
\end{figure*}

%\subsubsection{Single Snapshots: SFR-Mach-$\alpha_{\rm vir}$ Relation}
%%M~ 30 in normal spirals \citep{McKee99a}
%%M~ 100 in SBs \citep{Downes98a}
%In the following, SFR of each MC is calculated by integrating over the recent \SF history of stars within each MC. 
%More specifically, we sum up all the stellar masses with stellar age of $<$10\,Myr and  normalized 
%the mass over this period of time.
%In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular
%complexes identified.
%We find a positive correlation between the two quantities, with a Pearson-$R$ coefficient of xxx,
%which is unsurprising given that our simulations include the effect of stellar feedback. That is,
%the high $\mathcal{M}$ can be interpreted as a result of \SF resulting from feedback from
%massive stars.

@@

%\begin{figure*}[tbph]
% \centering
%\includegraphics[width=\textwidth]{\figpath/.pdf}
%\caption{\label{fig:}}
%\end{figure*}

@@

The range of masses of the MCs identified are comparable to those observed in \z$\sim$2 galaxies in $i$-band 
(i.e., rest-frame visible), which is between $M_{\rm cl}\approx$10$^{6.5-9xx}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.
Observational studies often report the mass distribution in the form of a cumulative function (CMF).
While the CMF of the MCs is quite noisy due to resolution effect and since we only have one galaxy here 
in the cosmological zoom-in simulation, we could improve the ``signal-to-noise ratio'' by including 
MCs identified from the different snapshots\footnote{This approach is valid unless in some snapshots,
the galaxy experience a violent event, which is relatively rare across the few 100\,Myr studied here.}.
We show the resulting CMF in \Fig{cmf}.
Motivated by the observational study by \citealt{Blitz07a}, we fit a power-law to the CMF, which is expressed in the form of:
\begin{equation}
n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
\end{equation}
where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 
for MCs identified using the lowest and the highest $n_{\rm cut}$ adopted in this study.
The uncertainties here are the formal fitting uncertainties.
Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
{\bf This means ....}

>>>>

The growth of galaxies and their subsequent evolution are governed by the baryon cycle ---
galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive blackholes)
and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
The general consensus is that the growth of \highz galaxies are triggered and supported by massive
gas inflows from mergers and/or the cosmic web at early cosmic time, when the IGM and galaxies themselves 
are more gas-rich in their star-forming molecular
gas contents compared to present-day galaxies.
% while at a given snapshot, the gas mass fraction maybe low (esp. at high-z when
% the gravitational potential is still increasing), but their gas reservoirs
% are continuously being replenished.
These massive gas inflows in turn trigger gravitational instability and lead
to the formation of gas structures that are typically more massive and denser than those
observed in nearby galaxies, with masses of $M_{\rm cl}$\eq10$^9$\,\Msun
and sizes on sub-kpc scales (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
Some theoretical works argue that the
migration of such giant massive clumps are responsible for contributing to the
buildup of the bulges of massive galaxies at \z$\sim$0 \citep[e.g.,][]{Ceverino10a}.

@@

As we increase the density threshold, some of the MC within the main disk break
into multiple sub-MCs.
As such, we effectively identify a population of denser molecular structures  (\Fig{MC}).
This population of sub-MCs has dynamics largely
similar to those observed
in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in
terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see
e.g., \citealt{Swinbank11a}),
with sizes of the order of $R\simeq$100\,pc and velocity
dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. 
As shown in \Fig{alpha16}, their virial parameter ($\alpha_{\rm vir}\gtrsim10$)
are lower than their ``parent'' MCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$). 
%We note that previous studies by 
%\citealt{Dobbs08a} and \citealt{Tasker09a} report that
%clouds form in galactic disk typically have virial parameters between $\alpha_{\rm vir}$\eq0.2$-$10.
This is consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally non-collapsing structures,
which are supported by turbulence and rotation.
In fact, based on the virial parameter, the MC identified in (the densest region of) the main disk of \flower
would indicate that the MC itself is gravitationally unbound and is supported/confined 
by turbulence and rotation on large scales.
On the other hand, the MCs in the satellite galaxies are found to have
lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
with $\alpha_{\rm vir}\simeq$1 (see top panels of \Fig{alpha16} and \Fig{alpha27}).
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). 
Given the low virial parameter
and the $\sigma^2/R - \Sigma$ relation found for the MCs of the satellite galaxies, 
these structures are likely collapsing structures.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
\caption{
Larson's (linewidth-size) relation of \flower in
accreting phase (top) and
starburst phase (bottom) compared to
those observed in nearby and the \z$\sim$2 star-forming galaxy.
% Red lines show the relation obtained from \citet{}.
Literature data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accreting phase (star symbols) compared to those observed in the Milky Way.
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
compared to those observed in the Milky Way (black dot markers).
The V-shaped dashed lines show the locii along which the given external pressures
are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
In both panels, the star symbols are color-coded by $n_{\rm cut}$.
Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
and the locus of $\log{P/\textrm{K cm}^{-3} = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
\label{fig:alpha16}}
\end{figure*}

@@

We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accreting phase (see \Sec{sfh})
compared to the 
observational data of molecular clouds in the Milky Way associated with massive \SF 
\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained based on 
Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein),
which we extrapolate to match the mass and size scales of the MCs of \flower.
By comparing the masses and sizes found in clouds with and without massive \SF ($<$10\,\Msun) 
in the Milky Way, \citet{Kauffmann10c} report a 
mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
at a given radius. As shown in \Fig{MR}, the MCs identified in the accreting phase of \flower lie above this relation, along the locus 
with a visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
On the other hand, the MCs of \flower lie below the locus of $A_V$\eq100\,mag that the Milky Way clouds follow.
{\bf This may suggest ....}
We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
parameter space as the accreting phase. 
{\bf so...}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accreting phase of \flower in our simulation (star symbols) 
compared to observational data of molecular clouds in the Milky Way associated with massive \SF 
(magenta circles, green stars, blue dots, and black triangles) and empirical relations 
established based on \obs of the Milky Way.
Star symbols are color-coded by increasing $n_{\rm cut}$.
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
\label{fig:MR}}
\end{figure*}

@@

@@

The mass range of the MCs identified in our simulation is $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun,
consistent with those observed in \z$\sim$2 galaxies in
rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
Observational studies in the nearby Universe, where 
spatially resolution are better at revealing molecular (sub-)structures,
often report the mass distribution of molecular clouds in the form of a cumulative function (CMF).
While the CMF of the MCs for a given snapshot of our simulation is 
quite noisy, since we have only one (main) galaxy, 
we could improve the ``signal-to-noise ratio'' by including 
MCs identified across all snapshots\footnote{This approach is valid unless in some snapshots,
the galaxy experience a violent event, which is relatively rare across the 700\,Myr studied here.}.
We show the resulting CMF in \Fig{cmf}.

Motivated by the observational study by \citealt{Blitz07a}, we fit a power-law to the CMF, which is expressed in the form of:
\begin{equation}
n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
\end{equation}
where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 by adopting the lowest and the highest $n_{\rm cut}$ studied here.
The uncertainties are the formal fitting uncertainties.
Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
This difference in slopes suggest that mo, albeit speculative due to resolution effects.
In particular, it is possible that we may identify more substructures/smaller and less massive MCs if our simulation 
was of higher resolution (but one must acknowledge that ..... is expeneisve to do zoom-in. This is what we have at best at the 
moment with simulation power).
That said, simularly massive moleuclar clouds have been reported in simulations of higher resolution (i.e., not zoom-in; \citealt{}).
It is therefore conceivable that our results are not that far off.
